### 2021-05-02 doc/VerticalArrangements.tex
teaked cost graph so that it only summarized all firms and party cost changes. also changed the figure desciption in text

\begin{sidewaysfigure}
\centering
\includegraphics[scale=0.9]{../output/surplussum_cost.png}
\caption{The figure displays box and whisker plots summarizing the extent to which merger outcomes change according to 6 different cost scenarios. Dark blue boxes (``Party Constant") assume that the merging parties face constant marginal costs while other firms face linear marginal costs. Orange boxes (``Constant") assume that all firms face constant marginal costs. Light grey boxes (``Constant/Linear") assume upstream firms have constant marginal costs, while downstream firms have linear marginal costs. Orange box depicts the effects assuming that firms face linear marginal costs. Whiskers depict the $5^{th}$ and $95^{th}$ percentiles of a particular outcome, boxes depict the $25^{th}$ and $75^{th}$ percentiles, and the solid horizontal line depicts the median. }
\label{fig:surplussumcost}
\end{sidewaysfigure}
\end{document}

>>>>

\begin{sidewaysfigure}
\centering
\includegraphics[scale=0.9]{../output/surplussum_cost.png}
\caption{The figure displays box and whisker plots summarizing the extent to which merger outcomes change according to 4 different cost scenarios. The boxes in the top row (``All") either assume all firms face either constant marginal costs (blue,left) or linear marginal costs (orange, right). The boxes in the bottom row (``Party") eitehr assume that the merging parties face constant marginal costs while other firms face linear marginal costs (blue, left), or the merging parties face linear marginal costs while other firms face constant marginal costs (orange, right). Whiskers depict the $5^{th}$ and $95^{th}$ percentiles of a particular outcome, boxes depict the $25^{th}$ and $75^{th}$ percentiles, and the solid horizontal line depicts the median. }
\label{fig:surplussumcost}
\end{sidewaysfigure}
\end{document}
